---
title: "Alcohol vs Seat choice"
author: "Martha Leal Olmedo"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The plot shows a huge difference between the back row and the front row, it also shows a big difference in the back row and the middle row.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

According to the chart the back row drinks 8 in a half drinks per week, the front row drinks 1 in a half drinks per week, and the middle row drinks 3 thirds of a drink per week, so overall the back row drinks more drinks per week compared to the front and middle rows, due to this it's reasonable to assume they aren't drinking the same amount.

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value represents the chances of getting a result that we just obtained, if the null hypothesis is actually true. Since the result is small I am going to reject the hypothesis.
We now need to try and discover what is the difference from the other.
```{r}
plot(TukeyHSD(model1))
```

According to this chart the front and middle rows do not have a difference but the front-back and back-middle are difference.

## Conclusions


