---
title: "Alcohol vs Seat choice"
author: "Martha Leal Olmedo"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

According to the chart the back row drinks 8 in a half drinks per week, the front row drinks 1 in a half drinks per week, and the middle row drinks 3 thirds of a drink per week, so overall the back row drinks more drinks per week compared to the front and middle rows, due to this it's reasonable to assume they aren't drinking the same amount.

## Inferential Tests

## Conclusions


